An enhancer code compendium of early human neuronal and neural crest development

### 2025-04-08 manuscript.tex
Summary and keywords.

%Context
Enhancers encode cell types and cell states using 
%need
%task
%results
%conclusion
%implication

@@

>>>>

%Context
Enhancers encode cell types as clusters of transcription factor binding sites. 
%need
Studies of enhancer-codes are predominantly limited to a small number of cell types at a time and often focus
on model organisms.
%task and results
In this study we generate a single-cell multiome atlas of differentiating human neural tube organoids 
and of the head of a four weeks post conception human embryo. 
Using DNA sequence based deep learning - DeepNeuralTube - we identify a total of 15 cell types that 
are in common between the organoid model and the human embryo and we provide a compendium of enhancer-codes 
for each individual cell type. 
We confirm the paradigm that enhancers are encoded using heterotypic clusters of 4-5 transcription factor binding sites in a single nucleosome depleted region. 
Enhancers encoding anterior-posterior patterning, however, form a exception to this rule where they are encoded using
homotypic clusters of homeodomain transcription factor binding sites.
%conclusion
%implication

@@

Enhancer-code, human neural tube, human development, deep learning, sequence-to-function
